si: code and prose exploring Spatial Interaction models

### 2022-04-22 README.qmd
Update with tidyeval example
Former-commit-id: 854122a5dca7e0601224aeb74d6d244f34de0660

```{r distance}
library(si)
# prepare OD data
od = si_to_od(
  origins = si_zones,        # origin locations
  destinations = si_zones,   # destination locations
  max_dist = 5000            # maximum distance between OD pairs
  )
# specify a function
gravity_model = function(od, beta) {
  od[["origin_all"]] * od[["destination_all"]] *
    exp(-beta * od[["distance_euclidean"]] / 1000)
} 
# perform SIM
od_res = si_calculate(od, fun = gravity_model, beta = 0.3, constraint_p = origin_all)
# visualize the results
plot(od_res$distance_euclidean, od_res$interaction)
```

>>>>

```{r distance}
library(si)
library(dplyr)
# prepare OD data
od = si_to_od(
  origins = si_zones,        # origin locations
  destinations = si_zones,   # destination locations
  max_dist = 5000            # maximum distance between OD pairs
  )
# specify a function
gravity_model = function(beta, d, m, n) {
  m * n * exp(-beta * d / 1000)
} 
# perform SIM
od_res = si_calculate(
  od,
  fun = gravity_model,
  d = distance_euclidean,
  m = origin_all,
  n = destination_all,
  constraint_p = origin_all,
  beta = 0.3
  )
# visualize the results
plot(od_res$distance_euclidean, od_res$interaction)
```

Note: this approach also allows you to use {si} functions in {dplyr} pipelines:

```{r}
od_res = od %>% 
  si_calculate(fun = gravity_model, 
               m = origin_all,
               n = destination_all,
               d = distance_euclidean,
               beta = 0.3)
od_res %>% 
  select(interaction) %>% 
  plot()
```
